Title of My Article\titlelinebreak{} with a Forced Linebreak

### 2013-06-27 mt-marathon.2012/PBML_article.tex
from google doc

\section{Scoring}
\subsection{Old Framework}

>>>>

\section{Scoring}
\subsection{Old Framework}
The types of feature functions were hardcoded when evaluating the scores of translation rules and hypotheses. For example, a translation rule is scored according to Equation (1)

\begin{equation}
%  score = Sum_i _member_T(weight_i * score_i) + Sum_i _member_L(weight_i * score_i) + weight_wp * word-penalty
\end{equation}

where T is the set of translation models, and L is the set of sequence models.

Similarly, when evaluating a hypothesis, the score is calculated as follows:

\begin{equation}
% score =  Sum_i _member_T(weight_i * score_i)
%    + Sum_i _member_L(weight_i * score_i)
%    + weight_wp * word-penalty
%    + weight_d * score_d
%    + Sum_i _member_R(weight_i * score_i)
%    + future_score
\end{equation}

where $weight_d$ and $score_d$ is the distortion weight and score respectively, R is the set of lexicalized reordering models.

When adding a new feature function, it would not be included in the scoring of the translation rule and hypotheses until Equation (1) and (2) are update.

Translation rule always evaluated occurs before decoding, either during loading of the feature function, or just before the translation rule is used in decoding.

Hypotheses are evaluated when they are created during the search process.

\subsection{New Framework}
The new framework better supports the creation of arbitary feature functions by generalizing all code that deals with feature functions.

Equation (1) becomes Equation (...)
\begin{equation}
%  score = Sum_i _member_FF(weight_i * score_i)
\end{equation}

where FF is the set of feature functions.

Equation (2) becomes Equation (...)
\begin{equation}
%  score =  Sum_i _member_FF(weight_i * score_i)
%  + future_score
\end{equation}

Furthermore, there are three places where each feature function can be evaluated. At each place, a different range of information is available to the feature function to access for information.

    1. During creation of translation rules. Access to the words in the source and target side of translation rule.

    2. Just before decoding. Access to the entire source sentence to be decoded.

    3. During decoding. Access to the context information is available, containing the hypotheses create to translate the sentence so far. The exact information contained in the hypotheses is dependent on whether the formalism used.

Scores that are evaluated at stage one can be cached and reused inter-sentence. Scores evaluted during stage (2) and (3) cannot be cached as they depend on the entire source sentence. Therefore, it is more efficient to evaluate as early as possible.

Each feature function can override any or all of the method to evaluate at each of these stage. For example. a simple word penalty feature would typically implement its evaluation in stage (1) as access to the translation rule is sufficient information to allow it to evaluate the word penalty score.

On the other hand, a feature that depends on the bag of words of the input sentence would override the method for stage (2).

Stateful features, and features that depend on the segmentation of the input sentence, need to override stage (3).

The most efficient way to implement language models is to override stage (1) and (3). As a stateful feature, it must override stage (3) to access adjacent target words to score overlapping n-grams. However, it is able to score the n-grams within each translation rule, and also calculate the estimated future cost, without the context. By evaluating the stateless portion of the language model score during stage (1) mitigate these score from having to be re-evaluated each time the translation rule is applied. This behaviour codify the existing practises by building the framework to support it, alllowing other feature function to take advantage of this efficient mechanism.

Additionally, some feature functions do not override any of the stages. These feature is so intertwined with the search operation that their scores are set by search operation themselves. The feature function exist as an identifier to locate the score. Features functions such as the translation models, unknown word penalty, and generation models score fall into this category.

\subsection{CDEC and Joshua}
Moses implements a one-pass search strategy. All feature functions are evaluated when a hypothesis is created.

Joshua and CDEC employs a multi-pass search strategy to translate each sentence. Each pass creates a hypergraph that is used as the input for the next pass. Both decoders evaluates stateless feature functions in the first pass, then stateful feature functions in the second.

CDEC also supports an arbitary number of passes and split the feature functions between those passes.

\section{File Format}
\subsection{Old Framework}
Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section

  [ttable-file]

Language models in

  [lmodel-file]

Furthermore, feature function also need a separate weight section, for example, for translation models:

  [weight-t]

and language models:

 [weight-l]

New feature functions need to create and manage their own specification and sections.

The features that can be tuned by MERT is also hardcoded in the tuning script. The MERT script has to be altered every time a new feature function is integrated into Moses.

\subsection{New Framework}
The configuration file format has been changed to minimize the amount of boilerplate code necessary when adding new feature functions. All feature functions are declared in the configuration file in the section

  [feature]

In the fixed format

  Feature-Name [key=value]*

For example,

  KENLM factor=0 path=lm.arpa order=5

All dense weights are put into the section

  [weight]

In the fixed format

  Feature-Instance= [value]*

Similarly, weights for sparse features are in separate file referenced by the section

  [weight-file]

in the format
  Feature-Instance\_feature value

\section{Sparse Feature Function}

Sparse features contain scores that may only be present occasionally. Also, there may be many more sparse features than dense features. There are typically 12 scores in a standard phrase-based model and 8 scores in a hierarchical phrase-based model. There may be millions of sparse score in a system with sparse features. However, only a few will be present in a particular hypothesis.

This presents efficiency challenges which each decoder has attempted to solve in a different way.

\subsection{Moses}
Moses explicitly implements both dense and sparse features, and each score must be identifiable as one or the other.
The intuition behind this is that most systems will still contain dense features, with a smattering of sparse features. Therefore, it would be more efficient to use dedicated
